#GA monthly report - Audio

##one known issue:with or without segment, user and all users are not matching with dashboard

```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
##auth

library(googleAnalyticsR)
library(googleAuthR)
##service_token <- gar_auth_service(json_file="C:\\Users\\Random\\Downloads\\R-40e8fcb3b34b.json")
Sys.setenv(GA_AUTH_FILE='C:\\Users\\zhanzhuo.AUTH\\Downloads\\R-3b6ace1ed38c.json')




options(googleAuthR.client_id = "6825601687-p6qn50ihi2pii5nv6boh3h5gbp6d5u2n.apps.googleusercontent.com")
options(googleAuthR.client_secret = "3b6ace1ed38cba6d8840d9bc63fa03da01cc1629")
options(googleAuthR.scopes.selected = "https://www.googleapis.com/auth/analytics")
ga_auth()

##save view id for JumpStart
##account_list <- ga_account_list()
##ga_id <- account_list[17,'viewId']
ga_id<-"117489773"
##meta <- google_analytics_meta()
##choose JS production segment
##my_segments <- ga_segment_list()
##segs <- my_segments$items
##segs[,c("name","id","defintion")]
segment_for_call <- "gaid::Nxk3WGL_T4-cQT3yLiEgIA"



## make Audio segment elements
# con1 <-segment_element("appVersion", 
#                       operator = "REGEXP", 
#                       type = "DIMENSION", 
#                       scope = "SESSION",
#                       expressions="1.0.105.0|1.0.111.0|1.0.137.0|1.0.138.0")
# con2 <-segment_element("country", 
#                       operator = "REGEXP", 
#                       type = "DIMENSION", 
#                       expressions="china|germany|korea", 
#                       caseSensitive = FALSE,
#                       scope = "SESSION",
#                       not=TRUE)
# con3 <-segment_element("ga:dimension1", 
#                       operator = "REGEXP", 
#                       type = "DIMENSION", 
#                       scope = "SESSION",
#                       expressions="china|germany|korea", 
#                       caseSensitive = FALSE,
#                       not = TRUE)
# sv_simple1 <- segment_vector_simple(list(list(con1)))
# sv_simple2 <- segment_vector_simple(list(list(con2)))
# sv_simple3 <- segment_vector_simple(list(list(con3)))
# 
# 
# seg_defined <- segment_define(list(sv_simple1,sv_simple2,sv_simple3))
##seg_defined <- segment_define(list(sv_simple1))

##seg_obj <- segment_ga4("Audio Production Segment", user_segment = seg_defined)


seg_obj <- segment_ga4("audio", segment_id = segment_for_call)
##meta2 <-meta[,c("name","type","status","uiName","group","description")]

startDate<-"2018-02-25"
endDate<-"2018-03-10"

#month_or_week<-"ga:yearMonth"
month_or_week<-"ga:week"

```
The date range is from `r startDate` to `r endDate`.


##First time launch (new users) in 'K

```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


AudioNewUsers <- google_analytics(ga_id, 
                                    c(startDate,endDate), 
                                    dimensions=c(month_or_week), 
                                    segments = seg_obj, 
                                    metrics = c('newUsers','users')
                                    ##anti_sample = TRUE
                                    )
```
`r format(AudioNewUsers[,"newUsers"], digits=10, big.mark=",")`



## Avg speaker selections per active user per month
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_speaker <- dim_filter("eventAction","EXACT","SelectOutputDevice",caseSensitive = FALSE,not = FALSE)

fc_exact_speaker <- filter_clause_ga4(list(df_exact_ea_speaker))
avgSpeakerSelection <- google_analytics(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users','totalEvents'),
                                              dim_filters = fc_exact_speaker
                                              ##anti_sample = TRUE
)
```
`r format(avgSpeakerSelection[,"totalEvents"]/avgSpeakerSelection[,"users"], digits=10, big.mark=",")`

## Avg microphone selections per active user per month
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_micro <- dim_filter("eventAction","EXACT","SelectInputDevice",caseSensitive = FALSE,not = FALSE)

fc_exact_micro <- filter_clause_ga4(list(df_exact_ea_micro))
avgMicroSelection <- google_analytics(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users','totalEvents'),
                                              dim_filters = fc_exact_micro
                                              ##anti_sample = TRUE
)
```
`r format(avgMicroSelection[,"totalEvents"]/avgMicroSelection[,"users"], digits=10, big.mark=",")`



##Active Users in 'K
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

activeUsers  <- google_analytics(ga_id, 
                                        c(startDate,endDate), 
                                        segments = seg_obj, 
                                        dimensions=c(month_or_week), 
                                        metrics = c('users','newUsers')
                                        ##anti_sample = TRUE
)
```
`r format(activeUsers[,"users"], digits=10, big.mark=",")`

##Returning users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret <- dim_filter("userType","EXACT","Returning Visitor",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
Returningusers <- google_analytics(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`




