#GA monthly report - OMEN

##one known issue:with or without segment, user and all users are not matching with dashboard

```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
##auth

library(googleAnalyticsR)
library(googleAuthR)
##service_token <- gar_auth_service(json_file="C:\\Users\\Random\\Downloads\\R-40e8fcb3b34b.json")
Sys.setenv(GA_AUTH_FILE='C:\\Users\\zhanzhuo.AUTH\\Downloads\\R-3b6ace1ed38c.json')




options(googleAuthR.client_id = "6825601687-p6qn50ihi2pii5nv6boh3h5gbp6d5u2n.apps.googleusercontent.com")
options(googleAuthR.client_secret = "3b6ace1ed38cba6d8840d9bc63fa03da01cc1629")
options(googleAuthR.scopes.selected = "https://www.googleapis.com/auth/analytics")
ga_auth()

##save view id for JumpStart
##account_list <- ga_account_list()
##ga_id <- account_list[17,'viewId']
ga_id<-"120376362"
ga_JumpStart_id<-"116132142"

##meta <- google_analytics_meta()
##choose JS production segment
##my_segments <- ga_segment_list()
##segs <- my_segments$items
##segs[,c("name","id","defintion")]
segment_for_call <- "gaid::X5Y0S8WHTXK5DCKDp1J_QA"
segment_for_call_Jumpstart <- "gaid::2gdgrZsdSO-YaNjeD3vzeQ"





seg_obj <- segment_ga4("OMEN", segment_id = segment_for_call)
seg_obj_JumpStart <- segment_ga4("jumpstart", segment_id = segment_for_call_Jumpstart)

##meta2 <-meta[,c("name","type","status","uiName","group","description")]

launchDate<-"2017-06-01"

startDate<-"2018-02-25"
endDate<-"2018-03-10"

#month_or_week<-"ga:yearMonth"
month_or_week<-"ga:week"


```
The date range is from `r startDate` to `r endDate`.



##OMEN booted units in 'K (from JumpStart)

```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_reg_cd4 <- dim_filter("ga:dimension23","REGEXP","omen",caseSensitive = FALSE,not = FALSE)
fc_reg_cd4 <- filter_clause_ga4(list(df_reg_cd4),operator = "AND")

OMENBooted <- google_analytics_4(ga_JumpStart_id, 
                                    c(startDate,endDate), 
                                    dimensions=c(month_or_week), 
                                    segments = seg_obj_JumpStart, 
                                    metrics = c('newUsers'),
                                    dim_filters = fc_reg_cd4
                                    ##anti_sample = TRUE
                                    )


```
`r format(OMENBooted[,"newUsers"], digits=10, big.mark=",")`



##First time launch (new users) in 'K

```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


OMENNewUsers <- google_analytics_4(ga_id, 
                                    c(startDate,endDate), 
                                    dimensions=c(month_or_week), 
                                    segments = seg_obj, 
                                    metrics = c('newUsers','users')
                                    ##anti_sample = TRUE
                                    )
```
`r format(OMENNewUsers[,"newUsers"], digits=10, big.mark=",")`





##cummulative launch units

```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


OMENNewUsers <- google_analytics_4(ga_id, 
                                    c(launchDate,endDate), 
                                    dimensions=c('appName'), 
                                    segments = seg_obj, 
                                    metrics = c('newUsers')
                                    ##anti_sample = TRUE
                                    )
```
`r format(OMENNewUsers[,"newUsers"], digits=10, big.mark=",")`





##Returning users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret <- dim_filter("userType","EXACT","Returning Visitor",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
Returningusers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`



##super Returning users >=3
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret1 <- dim_filter("ga:sessionCount","EXACT","1",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret2 <- dim_filter("ga:sessionCount","EXACT","2",caseSensitive = FALSE,not = TRUE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret1,df_exact_ut_ret2),operator="AND")
Returningusers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`


##All launches in 'K
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

AllLaunches  <- google_analytics_4(ga_id, 
                                        c(startDate,endDate), 
                                        dimensions=c(month_or_week), 
                                        segments = seg_obj, 
                                        metrics = c('users')
                                        ##anti_sample = TRUE
)
```
`r format(AllLaunches[,"users"], digits=10, big.mark=",")`

##Avg. seconds per session per month
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

AvgDurationandSessions <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("ga:avgSessionDuration")
                                          ##anti_sample = TRUE
)
```
`r format(AvgDurationandSessions[,"avgSessionDuration"], digits=10, big.mark=",")`



#Network

##eligible units - Network
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Network",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
eligibleNetworkUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleNetworkUsers<-eligibleNetworkUsers[,"users"]
```
`r format(eligibleNetworkUsers, digits=10, big.mark=",")`

##eligible units new- Network
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Network",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
eligibleNetworkUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("newUsers"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleNetworkUsers<-eligibleNetworkUsers[,"newUsers"]
```
`r format(eligibleNetworkUsers, digits=10, big.mark=",")`



##super Returning users >=3
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret1 <- dim_filter("ga:sessionCount","EXACT","1",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret2 <- dim_filter("ga:sessionCount","EXACT","2",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Network",caseSensitive = FALSE,not = FALSE)

fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret1,df_exact_ut_ret2,df_exact_ut_ret),operator="AND")
Returningusers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`

##eligible units - network-returning
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Network",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("userType","REGEXP","returning",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
networkreturn <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
networkreturn<-networkreturn[,"users"]
```
`r format(networkreturn, digits=10, big.mark=",")`


##Network -switched in users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","NetworkSpeed",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","AUTOModeClicked|CUSTOMModeClicked|OFFModeClicked",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
NetworkSwitched <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users","totalEvents"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(NetworkSwitched[,"users"], digits=10, big.mark=",")`

##Network -users who engage in mode/priority switching or block/unblock in the period - block was not instrumented
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","NetworkSpeed",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","AUTOModeClicked|CUSTOMModeClicked|OFFModeClicked|ChangeHigh|ChangeMedium",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","NetworkSpeed",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
NetworkSwitched <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users","totalEvents"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(NetworkSwitched[,"users"], digits=10, big.mark=",")`

##Network -switched in clicks

`r format(NetworkSwitched[,"totalEvents"], digits=10, big.mark=",")`






##Network -active users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","NetworkSpeed",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventCategory","REGEXP","NetworkSpeed",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
NetworkSwitched <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(NetworkSwitched[,"users"], digits=10, big.mark=",")`



#Macro key

##eligible units - Macro Key
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Keyboard|Macro",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
eligibleUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleUsers<-eligibleUsers[,"users"]
```
`r format(eligibleUsers, digits=10, big.mark=",")`

##eligible units new - Macro Key
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Keyboard|Macro",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
eligibleUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("newUsers"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleUsers<-eligibleUsers[,"newUsers"]
```
`r format(eligibleUsers, digits=10, big.mark=",")`

#super return - marcro key
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret1 <- dim_filter("ga:sessionCount","EXACT","1",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret2 <- dim_filter("ga:sessionCount","EXACT","2",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Keyboard|Macro",caseSensitive = FALSE,not = FALSE)

fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret1,df_exact_ut_ret2,df_exact_ut_ret),operator="AND")
Returningusers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`

##eligible units - macro-returning
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Keyboard|Macro",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("userType","REGEXP","returning",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
macroreturn <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
macroreturn<-macroreturn[,"users"]
```
`r format(macroreturn, digits=10, big.mark=",")`


##MacroKeys assign
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Macro_Keys",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","Assign",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","MacroKeys",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
MacroKeys <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users","totalEvents"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(MacroKeys[,"users"], digits=10, big.mark=",")`



##MacroKeys -active users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Macro_Keys",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventCategory","REGEXP","MacroKeys",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
NetworkSwitched <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(NetworkSwitched[,"users"], digits=10, big.mark=",")`



#lighting

##eligible units - Lighting
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
eligibleUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleUsers<-eligibleUsers[,"users"]
```
`r format(eligibleUsers, digits=10, big.mark=",")`


##eligible units new - Lighting
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
eligibleUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("newUsers"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleUsers<-eligibleUsers[,"newUsers"]
```
`r format(eligibleUsers, digits=10, big.mark=",")`

##eligible units - Lighting-returning
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("userType","REGEXP","returning",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
lightingreturn <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
lightingreturn<-lightingreturn[,"users"]
```
`r format(lightingreturn, digits=10, big.mark=",")`

#super return - lighting
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret1 <- dim_filter("ga:sessionCount","EXACT","1",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret2 <- dim_filter("ga:sessionCount","EXACT","2",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)

fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret1,df_exact_ut_ret2,df_exact_ut_ret),operator="AND")
Returningusers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`


##lighting -mode switches/apply/apply to all/brightness in users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","ModeClicked|Apply|BrightnessClicked|DurationClicked",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
OCIntelApplied <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users","totalEvents"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
```
`r format(OCIntelApplied[,"users"], digits=10, big.mark=",")`

##lighting -mode switches/apply/apply to all/brightness in clicks

`r format(OCIntelApplied[,"totalEvents"], digits=10, big.mark=",")`




##lighting -active users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Lighting",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
NetworkSwitched <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(NetworkSwitched[,"users"], digits=10, big.mark=",")`


#OC

##eligible units - OC
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","over_clock|Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret),operator="AND")
eligibleUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleUsers<-eligibleUsers[,"users"]
```
`r format(eligibleUsers, digits=10, big.mark=",")`

##eligible units new - OC
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","over_clock|Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret),operator="AND")
eligibleUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("newUsers"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
eligibleUsers<-eligibleUsers[,"newUsers"]
```
`r format(eligibleUsers, digits=10, big.mark=",")`

##eligible units - oc-returning
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","over_clock",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("userType","REGEXP","returning",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2),operator="AND")
ocreturn <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
ocreturn<-ocreturn[,"users"]
```
`r format(ocreturn, digits=10, big.mark=",")`


#super return - OC
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ut_ret1 <- dim_filter("ga:sessionCount","EXACT","1",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret2 <- dim_filter("ga:sessionCount","EXACT","2",caseSensitive = FALSE,not = TRUE)
df_exact_ut_ret <- dim_filter("ga:dimension5","REGEXP","over_clock",caseSensitive = FALSE,not = FALSE)

fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret1,df_exact_ut_ret2,df_exact_ut_ret),operator="AND")
Returningusers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ret
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`


##OC -applied
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Overclocking_Intel|Overclocking_AMD",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","Apply",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
OCIntelApplied <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
OCIntelApplied<-OCIntelApplied[,"users"]
```
`r format(OCIntelApplied, digits=10, big.mark=",")`

##OC -applied or ran benchmark
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Overclocking_Intel|Overclocking_AMD",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","Apply|RunBenchmark",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
OCIntelApplied <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
OCIntelApplied<-OCIntelApplied[,"users"]
```
`r format(OCIntelApplied, digits=10, big.mark=",")`

##OC -ran benchmark
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Overclocking_Intel|Overclocking_AMD",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","RunBenchmark",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
OCIntelApplied <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
OCIntelApplied<-OCIntelApplied[,"users"]
```
`r format(OCIntelApplied, digits=10, big.mark=",")`

##OC -applied
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Overclocking_Intel|Overclocking_AMD",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret2 <- dim_filter("eventAction","REGEXP","Apply",caseSensitive = FALSE,not = FALSE)
df_exact_ut_ret3 <- dim_filter("eventCategory","REGEXP","Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret,df_exact_ut_ret2,df_exact_ut_ret3),operator="AND")
OCIntelApplied <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)
OCIntelApplied<-OCIntelApplied[,"users"]
```
`r format(OCIntelApplied, digits=10, big.mark=",")`



##OC -active users
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ut_ret <- dim_filter("ga:dimension19","REGEXP","Overclocking",caseSensitive = FALSE,not = FALSE)
fc_exact_ret <- filter_clause_ga4(list(df_exact_ut_ret))
NetworkSwitched <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c(month_or_week), 
                                          segments = seg_obj, 
                                          metrics = c("users"),
                                          dim_filters = fc_exact_ret
                                          ##anti_sample = TRUE
)

```
`r format(NetworkSwitched[,"users"], digits=10, big.mark=",")`

