#GA report - JumpStart
  

<!-- Limitations -->

<!-- As with daily walk anti-sample techniques, user metrics and unique users are linked to the date range you are querying, so this technique will not match the numbers as if you queried over the whole date range. -->


```{r main-block, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
##auth
# test

library(googleAnalyticsR)
library(googleAuthR)
library(httr)
##service_token <- gar_auth_service(json_file="C:\\Users\\Random\\Downloads\\R-40e8fcb3b34b.json")
Sys.setenv(GA_AUTH_FILE='C:\\Users\\zhanzhuo.AUTH\\Downloads\\R-3b6ace1ed38c.json')

set_config(config(ssl_verifypeer = 0L))



options(googleAuthR.client_id = "6825601687-p6qn50ihi2pii5nv6boh3h5gbp6d5u2n.apps.googleusercontent.com")
options(googleAuthR.client_secret = "3b6ace1ed38cba6d8840d9bc63fa03da01cc1629")
options(googleAuthR.scopes.selected = "https://www.googleapis.com/auth/analytics")

ga_auth()

##set date range
launchDate<-"2016-05-01"
startDate<-"2018-02-25"
endDate<-"2018-03-10"

#month_or_week<-"ga:yearMonth"
month_or_week<-"ga:week"


##save view id for JumpStart
##account_list <- ga_account_list()
##ga_id <- account_list[17,'viewId']
ga_id<-"116132142"
##meta <- google_analytics_meta()
##choose JS production segment
##my_segments <- ga_segment_list()
##segs <- my_segments$items
##segs[,c("name","id","defintion")]
segment_for_call <- "gaid::2gdgrZsdSO-YaNjeD3vzeQ"




seg_obj <- segment_ga4("JumpStart in field up to 378 (UWP ver)", segment_id = segment_for_call)
##meta2 <-meta[,c("name","type","status","uiName","group","description")]




```
The date range is from `r startDate` to `r endDate`.

# basic funnel

##Jumpstart New Users in 'K
```{r new-users, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

JumpstartNewUsers <- google_analytics_4(ga_id,
                                    c(startDate,endDate),
                                    dimensions=c(month_or_week),
                                    segments = seg_obj,
                                    metrics = c('newUsers')
                                    ##anti_sample = TRUE
                                    )
```
`r format(JumpstartNewUsers[,"newUsers"], digits=10, big.mark=",")`


##Jumpstart New Users app select 2c17+ and country list in 'K (RR justification)
```{r new-users-app-eligible, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_screen <- dim_filter("ga:dimension22","REGEXP","173|174|181",caseSensitive = FALSE,not = FALSE)
df_exact_screen1 <- dim_filter("ga:country","REGEXP","United States|United Kingdom|Australia|New Zealand",caseSensitive = FALSE,not = FALSE)
df_exact_screen2 <- dim_filter("ga:dimension23","REGEXP","Spectre",caseSensitive = FALSE,not = TRUE)
df_exact_screen5 <- dim_filter("ga:appVersion","REGEXP","1.1.165.0|1.1.158.0|1.0.144.0|1.0.141.0",caseSensitive = FALSE,not = TRUE)
df_exact_screen6 <- dim_filter("ga:dimension8","REGEXP","1.1.0.168|1.1.0.158|1.0.0.143|1.1.0.182|1.1.0.208|1.1.0.285",caseSensitive = FALSE,not = TRUE)
df_exact_screen7 <- dim_filter("ga:dimension24","REGEXP","Consumer|Premium",caseSensitive = FALSE,not = FALSE)



fc_exact_screen <- filter_clause_ga4(list(df_exact_screen,df_exact_screen1,df_exact_screen2,df_exact_screen5,df_exact_screen6,df_exact_screen7),operator = "AND")

JumpstartNewUsers <- google_analytics_4(ga_id,
                                    c(startDate,endDate),
                                    dimensions=c(month_or_week),
                                    segments = seg_obj,
                                    metrics = c('newUsers'),
                                    dim_filters = fc_exact_screen
                                    ##anti_sample = TRUE
                                    )
```
`r format(JumpstartNewUsers[,"newUsers"], digits=10, big.mark=",")`




##cummulative launch units

```{r cumulative-new-users, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


OMENNewUsers <- google_analytics_4(ga_id, 
                                    c(launchDate,endDate), 
                                    dimensions=c('appName'), 
                                    segments = seg_obj, 
                                    metrics = c('newUsers')
                                    ##anti_sample = TRUE
                                    )
```
`r format(OMENNewUsers[,"newUsers"], digits=10, big.mark=",")`




##Registration Screen shown in GA (in users)
```{r reach-reg-screen,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_screen <- dim_filter("screenName","EXACT","/register",caseSensitive = FALSE,not = FALSE)
fc_exact_screen <- filter_clause_ga4(list(df_exact_screen))
RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('users'),
                                              dim_filters = fc_exact_screen
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"users"], digits=10, big.mark=",")`


##HP Registration from HP OOBe consent = yes email=yes,  firstname=yes,  lastname = yes
```{r reg-in-1st-chance,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_screen2 <- dim_filter("ga:dimension14","EXACT","Yes",caseSensitive = FALSE,not = FALSE)
df_exact_screen3 <- dim_filter("ga:dimension20","EXACT","Valid",caseSensitive = FALSE,not = FALSE)
df_exact_screen4 <- dim_filter("ga:dimension18","EXACT","Valid",caseSensitive = FALSE,not = FALSE)
df_exact_screen5 <- dim_filter("ga:dimension19","EXACT","Valid",caseSensitive = FALSE,not = FALSE)



fc_eligible <- filter_clause_ga4(list(df_exact_screen2,df_exact_screen3,df_exact_screen4,df_exact_screen5),operator = "AND")


RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('newUsers'),
                                              dim_filters = fc_eligible
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"newUsers"], digits=10)`



##Registration eligible user consent = No,  eligible 1
```{r no-reg-part1,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_screen1 <- dim_filter("ga:dimension14","EXACT","Yes",caseSensitive = FALSE,not = TRUE)



fc_eligible <- filter_clause_ga4(list(df_exact_screen1))


RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('newUsers'),
                                              dim_filters = fc_eligible
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"newUsers"], digits=10)`


##Registration eligible user consent = Yes, email = no, eligible 2
```{r no-reg-part2,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_screen2 <- dim_filter("ga:dimension14","EXACT","Yes",caseSensitive = FALSE,not = FALSE)
df_exact_screen3 <- dim_filter("ga:dimension20","EXACT","Valid",caseSensitive = FALSE,not = TRUE)

fc_eligible <- filter_clause_ga4(list(df_exact_screen2,df_exact_screen3),operator = "AND")


RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('newUsers'),
                                              dim_filters = fc_eligible
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"newUsers"], digits=10)`




##HP Jumpstart Registration (2nd chance registration)
```{r reg-2nd-chance,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ec <- dim_filter("eventCategory","EXACT","Register",caseSensitive = FALSE,not = FALSE)
df_exact_ea <- dim_filter("eventAction","EXACT","HPAccountRegistered",caseSensitive = FALSE,not = FALSE)
fc_exact_registered <- filter_clause_ga4(list(df_exact_ec,df_exact_ea),operator = "AND")
JumpstartRegistration <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('users'),
                                              dim_filters = fc_exact_registered
                                              ##anti_sample = TRUE
)
```
`r format(JumpstartRegistration[,"users"], digits=10, big.mark=",")`




##HP mcafee from HP OOBe consent = yes email=yes
```{r mcafee-1st-chance,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_screen2 <- dim_filter("ga:dimension15","EXACT","Yes",caseSensitive = FALSE,not = FALSE)
df_exact_screen3 <- dim_filter("ga:dimension20","EXACT","Valid",caseSensitive = FALSE,not = FALSE)


fc_eligible <- filter_clause_ga4(list(df_exact_screen2,df_exact_screen3),operator = "AND")


RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('newUsers'),
                                              dim_filters = fc_eligible
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"newUsers"], digits=10)`



##mcafee eligible user consent = No  eligible 1
```{r no-mcafee-part1,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_screen1 <- dim_filter("ga:dimension15","EXACT","Yes",caseSensitive = FALSE,not = TRUE)



fc_eligible <- filter_clause_ga4(list(df_exact_screen1))


RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('newUsers'),
                                              dim_filters = fc_eligible
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"newUsers"], digits=10)`


##mcafee eligible user consent = Yes, email = no eligible 2
```{r no-mcafee-part2,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_screen2 <- dim_filter("ga:dimension15","EXACT","Yes",caseSensitive = FALSE,not = FALSE)
df_exact_screen3 <- dim_filter("ga:dimension20","EXACT","Valid",caseSensitive = FALSE,not = TRUE)

fc_eligible <- filter_clause_ga4(list(df_exact_screen2,df_exact_screen3),operator = "AND")


RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('newUsers'),
                                              dim_filters = fc_eligible
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"newUsers"], digits=10)`



##Jumpstart McAfee Registrations
```{r mcafee-2nd-chance,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ec_ma <- dim_filter("eventCategory","EXACT","Register",caseSensitive = FALSE,not = FALSE)
df_exact_ea_ma <- dim_filter("eventAction","EXACT","McAfeeRegistered",caseSensitive = FALSE,not = FALSE)
fc_exact_registered_ma <- filter_clause_ga4(list(df_exact_ec_ma,df_exact_ea_ma),operator = "AND")
JumpstartMcAfeeRegistrations <- google_analytics_4(ga_id,
                                            c(startDate,endDate),
                                            dimensions=c(month_or_week),
                                            segments = seg_obj,
                                            metrics = c('users'),
                                            dim_filters = fc_exact_registered_ma
                                            ##anti_sample = TRUE
)
```
`r format(JumpstartMcAfeeRegistrations[,"users"], digits=10, big.mark=",")`


##McAfee Screen shown in GA (in users)
```{r reach-mcafee-screen,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_screen <- dim_filter("screenName","EXACT","/mcafee",caseSensitive = FALSE,not = FALSE)
fc_exact_screen <- filter_clause_ga4(list(df_exact_screen))
RegistrationScreenshown <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('users'),
                                              dim_filters = fc_exact_screen
                                              ##anti_sample = TRUE
)
```
`r format(RegistrationScreenshown[,"users"], digits=10, big.mark=",")`



##Jumpstart Dropbox Sign Up
```{r dropbox-signup,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_el_db <- dim_filter("eventLabel","EXACT","success",caseSensitive = FALSE,not = FALSE)
df_exact_ea_db <- dim_filter("eventAction","EXACT","Dropbox-Signup",caseSensitive = FALSE,not = FALSE)
fc_exact_registered_db <- filter_clause_ga4(list(df_exact_el_db,df_exact_ea_db),operator = "AND")
JumpstartDropboxSignUps <- google_analytics_4(ga_id,
                                                   c(startDate,endDate),
                                                   dimensions=c(month_or_week),
                                                   segments = seg_obj,
                                                   metrics = c('users'),
                                                   dim_filters = fc_exact_registered_db
                                                   ##anti_sample = TRUE
)
```
`r format(JumpstartDropboxSignUps[,"users"], digits=10, big.mark=",")`


##Monthly Active Users in 'K
```{r all-users,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

MonthlyActiveUsers  <- google_analytics_4(ga_id,
                                        c(startDate,endDate),
                                        dimensions=c(month_or_week),
                                        segments = seg_obj,
                                        metrics = c('users')
                                        ##anti_sample = TRUE
)
```
`r format(MonthlyActiveUsers[,"users"], digits=10, big.mark=",")`


##Returning users
```{r returning-users,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_usertype <- dim_filter("userType","EXACT","Returning Visitor",caseSensitive = FALSE,not = FALSE)
fc_exact_usertype <- filter_clause_ga4(list(df_exact_usertype))
Returningusers <- google_analytics_4(ga_id,
                                              c(startDate,endDate),
                                              dimensions=c(month_or_week),
                                              segments = seg_obj,
                                              metrics = c('users'),
                                              dim_filters = fc_exact_usertype
                                              ##anti_sample = TRUE
)
```
`r format(Returningusers[,"users"], digits=10, big.mark=",")`




##Avg. session duration per week
```{r avg-session-duration-byweek,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

AvgDurationandUsers <- google_analytics_4(ga_id,
                                          c(startDate,endDate),
                                          dimensions=c(month_or_week),
                                          segments = seg_obj,
                                          metrics = c("ga:avgSessionDuration")
                                          ##anti_sample = TRUE
)
AvgDurationandUsers[,"avgSessionDuration"]
```



##Avg. seconds of use per user per month
```{r avg-session-duration-bymonth,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

AvgDurationandUsers <- google_analytics_4(ga_id, 
                                          c(startDate,endDate), 
                                          dimensions=c('yearMonth'), 
                                          segments = seg_obj, 
                                          metrics = c("ga:sessionDuration","users")
                                          ##anti_sample = TRUE
)
AvgDurationPerUser<-AvgDurationandUsers[1,"sessionDuration"]/AvgDurationandUsers[1,"users"]
```
`r format(AvgDurationPerUser, digits=10, big.mark=",")`



# concierge


##cummulative panel clicks


```{r cum-panel-clicks,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_ea_panel_clk <- dim_filter("eventAction","EXACT","ContentClicked",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_clk <- filter_clause_ga4(list(df_exact_ea_panel_clk),operator = "AND")
MonthlyPanelClicks <- google_analytics_4(ga_id, 
                                    c(launchDate,endDate), 
                                    dimensions=c('appName'), 
                                    segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_ea_panel_clk
                                              ##anti_sample = TRUE
)
```
`r format(MonthlyPanelClicks[,"totalEvents"], digits=10, big.mark=",")`

##Online Concierge homepage screen shown (in users)
```{r reach-concierge-screen,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_panel_imp <- dim_filter("screenName","REGEXP","/OnlineConcierge|/OnlineConcierge-B",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_imp <- filter_clause_ga4(list(df_exact_ea_panel_imp),operator = "AND")
onlineConciergeScreenUsers  <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ea_panel_imp
                                              ##anti_sample = TRUE
)
```
`r format(onlineConciergeScreenUsers[,"users"], digits=10, big.mark=",")`


## panel impression in users - panel seen by user
```{r panel-seen-users,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_panel_imp <- dim_filter("eventAction","REGEXP","ContentExposed|PanelSeen",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_imp <- filter_clause_ga4(list(df_exact_ea_panel_imp),operator = "AND")
MonthlyPanelImpression  <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ea_panel_imp
                                              ##anti_sample = TRUE
)
```
`r format(MonthlyPanelImpression[,"users"], digits=10, big.mark=",")`

##panel received by user
```{r panel-received-users,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_panel_imp <- dim_filter("eventAction","REGEXP","ContentExposed|PanelReceived",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_imp <- filter_clause_ga4(list(df_exact_ea_panel_imp),operator = "AND")
MonthlyPanelImpression  <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ea_panel_imp
                                              ##anti_sample = TRUE
)
```
`r format(MonthlyPanelImpression[,"users"], digits=10, big.mark=",")`



## panel clicks in users
```{r panel-clicked-users,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_panel_clk <- dim_filter("eventAction","EXACT","ContentClicked",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_clk <- filter_clause_ga4(list(df_exact_ea_panel_clk),operator = "AND")
MonthlyPanelClicks   <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ea_panel_clk
                                              ##anti_sample = TRUE
)
```
`r format(MonthlyPanelClicks[,"users"], digits=10, big.mark=",")`

## Panel impresssion in clicks
```{r panel-received-clicks,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
df_exact_ea_panel_imp <- dim_filter("eventAction","REGEXP","ContentExposed|PanelReceived",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_imp <- filter_clause_ga4(list(df_exact_ea_panel_imp),operator = "AND")
MonthlyPanelImpression  <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_ea_panel_imp
                                              #anti_sample = TRUE
)
MonthlyPanelImpression[,"totalEvents"]
```


## Panel Clicks in clicks
```{r panel-cilced-clicks,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_panel_clk <- dim_filter("eventAction","EXACT","ContentClicked",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_clk <- filter_clause_ga4(list(df_exact_ea_panel_clk),operator = "AND")
MonthlyPanelClicks   <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_ea_panel_clk
                                              #anti_sample = TRUE
)
MonthlyPanelClicks[,"totalEvents"]

```







# App download

## Number of units with app download functions (all users)
```{r app-eligible-units-byflow,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_reg_cd34 <- dim_filter("ga:dimension34","REGEXP","AppInstall",caseSensitive = FALSE,not = FALSE)
fc_reg_cd34 <- filter_clause_ga4(list(df_reg_cd34),operator = "AND")
unitsWithAppdownload   <- google_analytics_4(ga_id, 
                                           c(startDate,endDate), 
                                           dimensions=c(month_or_week), 
                                           segments = seg_obj, 
                                           metrics = c('users','newUsers'),
                                           dim_filters = fc_reg_cd34 
                                           ##anti_sample = TRUE
)
```
`r format(unitsWithAppdownload[,"users"], digits=10, big.mark=",")`


## Number of units with app download functions (new users)

`r format(unitsWithAppdownload[,"newUsers"], digits=10, big.mark=",")`



##App download screen shown (in users)
```{r reach-app-screen,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}

df_exact_ea_panel_imp <- dim_filter("screenName","REGEXP","Appselect1|GetMoreApps|AppSelect_Page|GetMoreApps_Page",caseSensitive = FALSE,not = FALSE)
fc_exact_ea_panel_imp <- filter_clause_ga4(list(df_exact_ea_panel_imp),operator = "AND")
onlineConciergeScreenUsers  <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_ea_panel_imp
                                              ##anti_sample = TRUE
)
```
`r format(onlineConciergeScreenUsers[,"users"], digits=10, big.mark=",")`




## number of Users install apps successfully
```{r app-install-users,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_el_app <- dim_filter("eventLabel","EXACT","success",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app <- dim_filter("eventAction","EXACT","AppInstalled",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_el_app,df_exact_ea_app,df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('users'),
                                              dim_filters = fc_exact_install_app 
                                              ##anti_sample = TRUE
)
```
`r format(downloadinstallappsinUsers[,"users"], digits=10, big.mark=",")`


## Number of apps installed
```{r app-install-apps,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_el_app <- dim_filter("eventLabel","EXACT","success",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app <- dim_filter("eventAction","EXACT","AppInstalled",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_el_app,df_exact_ea_app, df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

```

#app operational view

## app selection in apps
## app selection in users

```{r app-select,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_ea_app <- dim_filter("eventAction","EXACT","AppSelected",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_ea_app, df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents','users'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

downloadinstallappsinUsers[,"users"]

```





## download attempts
```{r download-attempt,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_ea_app <- dim_filter("eventAction","EXACT","AppDownloaded",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_ea_app, df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

```



## download failure
```{r download-failure,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_el_app <- dim_filter("eventLabel","EXACT","fail",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app <- dim_filter("eventAction","EXACT","AppDownloaded",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_el_app,df_exact_ea_app,df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

```

## download cancel
```{r download-cancel,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_el_app <- dim_filter("eventLabel","EXACT","cancel",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app <- dim_filter("eventAction","EXACT","AppDownloaded",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_el_app,df_exact_ea_app,df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

```

## install attempt
```{r instal-attempt,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_ea_app <- dim_filter("eventAction","EXACT","AppInstalled",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_ea_app,df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

```


## install fail
```{r install-fail,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}


df_exact_el_app <- dim_filter("eventLabel","EXACT","fail",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app <- dim_filter("eventAction","EXACT","AppInstalled",caseSensitive = FALSE,not = FALSE)
df_exact_ea_app2 <- dim_filter("ga:dimension45","REGEXP","Live",caseSensitive = FALSE,not = FALSE)

fc_exact_install_app <- filter_clause_ga4(list(df_exact_el_app,df_exact_ea_app,df_exact_ea_app2),operator = "AND")
downloadinstallappsinUsers <- google_analytics_4(ga_id, 
                                              c(startDate,endDate), 
                                              dimensions=c(month_or_week), 
                                              segments = seg_obj, 
                                              metrics = c('totalEvents'),
                                              dim_filters = fc_exact_install_app
                                              #anti_sample = TRUE
)
downloadinstallappsinUsers[,"totalEvents"]

```
